Transforming Trash as an Artistic Act

### 2015-12-16 main.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999
Chapter review
Former-commit-id: f64723a83902ea5f39ee5e85800eba6ae02dbc92
Chapter 2 review
Former-commit-id: de9640209bade5dc3b51e32502a643f004e1026b

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
%\graphicspath{ {graphics/} }
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc]{appendix}
\usepackage[colorinlistoftodos]{todonotes}

@@

\setlength{\epigraphwidth}{.6\textwidth}
\setlength{\epigraphrule}{0pt}

@@

\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}
\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
\providecommand{\summary}[1]{\textcolor{green}{[#1]}}
\providecommand{\paraphrase}[1]{\textcolor{magenta}{\quotes{#1}}}
\renewcommand*\bibname{Bibliography}

@@

\begin{document}
\selectlanguage{english}
\begin{titlepage}
    \begin{center}

        \Huge
        Transforming Trash as an Artistic Act

        \vfill
        \Large
        A Master’s Thesis\\
        by\\
        Mustafa İlhan

        \vfill
        Department of\\
        Communication and Design\\
        İhsan Doğramacı Bilkent University\\
        Ankara\\
        \today

@@

\listoffigures
%{%
%\let\oldnumberline\numberline%
%\renewcommand{\numberline}{\figurename~\oldnumberline}%
%\listoffigures%
%}

@@

\pagenumbering{arabic}
\include{chapter1_reduced}
\include{chapter2_reduced}
\include{chapter3_reduced}
\include{chapter4_reduced}
\include{chapter5}
\bibliographystyle{apacite}
\bibliography{literature}
\begin{appendices}
\include{appendix_glossary}
\end{appendices}

>>>>

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,left=40mm,right=25mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
%\graphicspath{ {graphics/} }
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc]{appendix}
\usepackage[colorinlistoftodos]{todonotes}

@@

\usepackage[doublespacing]{setspace}

\usepackage{natbib}
\setlength{\bibsep}{0.0pt}

% Adding extra space between paragraphs
\setlength{\parskip}{\baselineskip}

% To align left todos
\reversemarginpar

% Chapter titles
\usepackage{titlesec}
\titleformat{\chapter}[display]
        {\normalfont\fontsize{14pt}{12pt}\centering\bfseries}{\MakeUppercase{\chaptertitlename}\  \thechapter}{2\baselineskip}{\uppercase}
\titleformat*{\section}{\bfseries\fontsize{12pt}{12pt}}
\titleformat*{\subsection}{\bfseries\fontsize{12pt}{12pt}}

% Chapter title spacing
\titlespacing{\chapter}{0pt}{25mm}{3\baselineskip}

% EPIGRAPH
\setlength{\epigraphwidth}{.6\textwidth}
\setlength{\epigraphrule}{0pt}

@@

\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}
\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
\providecommand{\summary}[1]{\textcolor{blue}{[#1]}}
\providecommand{\paraphrase}[1]{\textcolor{magenta}{\quotes{#1}}}

\addto\captionsenglish{%
  \renewcommand{\contentsname}{\MakeUppercase{Table of Contents}}%
  \renewcommand{\listtablename}{\MakeUppercase{List of Tables}}%
  \renewcommand{\listfigurename}{\MakeUppercase{List of Figures}}%
  \renewcommand{\bibname}{\MakeUppercase{Bibliography}}%
}

@@

\begin{document}
\selectlanguage{english}

\begin{titlepage}
    \begin{center}

        \singlespacing

        \vspace*{25mm}
        \uppercase{Transforming Trash as an Artistic Act}

        \vspace{15mm}
        A Master’s Thesis\\
        \vspace{15mm}
        by\\
        MUSTAFA İLHAN

        \vfill
        Department of\\
        Communication and Design\\
        İhsan Doğramacı Bilkent University\\
        Ankara\\
        \today
        \vspace{25mm}

\begin{titlepage}
    \begin{center}

        \singlespacing

        \vspace*{25mm}
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        \vspace*{4\baselineskip}
        Graduate School of Economics and Social Sciences\\
        of\\
		İhsan Doğramacı Bilkent University\\
		\vspace*{3\baselineskip}
        by\\
       	\vspace*{3\baselineskip}
        MUSTAFA İLHAN\\
        \vspace*{4\baselineskip}
        In Partial Fulfilment of the Requirements for the Degree of\\
		MASTER FINE OF ARTS\\
        \vspace{2\baselineskip}
        in\\
        \vspace{2\baselineskip}
        THE DEPARTMENT OF\\
        COMMUNICATION AND DESIGN\\
       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
        ANKARA\\
        \vspace{\baselineskip}
        January 2016

@@

\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
%{%
%\let\oldnumberline\numberline%
%\renewcommand{\numberline}{\figurename~\oldnumberline}%
%\listoffigures%
%}

@@

\pagenumbering{arabic}
\include{chapter1_reduced}
\include{chapter2_reduced}
\include{chapter3_reduced}
\include{chapter4_reduced}
\include{chapter5}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{apacite}
\bibliography{literature}
\begin{appendices}
\include{appendix_glossary}
\end{appendices}
